\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems

### 2024-03-28 TilingProjectDraft/tilingProject.tex
rewrote k-space RG in python

\section{Philosophy of auxiliary model methods}
The present method is a realisation of the general method of using simpler systems called auxiliary models to study bulk systems~\cite{martin_2016}. In general, a full Hamiltonian can be separated into the Hamiltonians for a particular subsystem \(S\), the rest of the system \(R\), and the interactions between \(S\) and \(R\).
\begin{equation}\begin{aligned}
	\mathcal{H} &= \mathcal{H}_S\ket{S}\bra{S} + \mathcal{H}_R \ket{R}\bra{R} + \mathcal{H}_{SR} \ket{S}\bra{R} + \mathcal{H}_{RS}\ket{S}\bra{R} \\
		    &= \begin{bmatrix} & \mathcal{H}_{R} && \mathcal{H}_{RS} & \\ & \mathcal{H}_{RS}^* && \mathcal{H}_{S} & \end{bmatrix}
\end{aligned}\end{equation}
where \(\ket{S}\) and \(\ket{R}\) actually represents sums over all basis kets of \(S\) and \(R\) respectively. As an example, we can split the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice as follows (fig.~\ref{cluster-bath}):
\begin{widetext}
\begin{equation}\begin{aligned}
	H_\text{hubb} &= \overbrace{U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}}^{H_S} + \underbrace{U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} -t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right)}_{H_R} -\underbrace{t^H\sum_{\sigma,\atop{i \in \text{N.N. of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)}_{H_{SR} + H_{RS}}\\
\end{aligned}\end{equation}
\end{widetext}
The Greens function of the full Hamiltonian can also be split in a similar fashion:
\begin{equation}\begin{aligned}
	G(\omega) = \begin{bmatrix} G_S && G_{SR} \\ G_{RS} && G_R \end{bmatrix}
\end{aligned}\end{equation}
Each Greens function can be written in terms of the non-interacting counterpart and the self-energy through the Dyson equation: \(\Sigma_i = 1/G_{i,0} - 1/G_i\).

@@

\subsubsection{Same symmetries in the Kondo coupling and bath interaction}
Assuming that both the Kondo interaction and the bath interaction couple to the \(d-\)wave channel, we have the microscopic functional forms 
\begin{equation}\begin{aligned}
	J^{(0)}_{{\bf k},{\bf q}} &= J f_\mathcal{D}({\bf k}) f_\mathcal{D}({\bf q})~,\\
	J^{(0)}_{{\bf \bar q},{\bf q}} &= J f_\mathcal{D}(\pi + {\bf q}) f_\mathcal{D}({\bf q}) = -Jf_\mathcal{D}({\bf q})^2 ~,
\end{aligned}\end{equation}
and
\begin{equation}\begin{aligned}
	W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} = -W f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf q})^2~,
\end{aligned}\end{equation}
where \(f_\mathcal{D}({\bf k}) = \cos\left( ak_{x} \right) - \cos\left( ak_y \right) \) is the \(d-\)wave symmetric functional form in \(k-\)space
The numerator of the RG equations becomes
\begin{equation}\begin{aligned}
	f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf q})^4\left[J^2 + 4JW\right] ~.
\end{aligned}\end{equation}
Since a factor of \(f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)\) factors out of the RG equation, the Kondo coupling will preserve its momentum dependence during the RG equation, and we can study the RG flow of the amplitude \(J\):
\begin{equation}\begin{aligned}
	\Delta J = \sum_{{\bf q} \in \text{PS}} \frac{-\left(J^2 + 4JW\right) f_\mathcal{D}({\bf q})^4}{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{2}f_\mathcal{D}({\bf q})^4}~.
\end{aligned}\end{equation}

\subsubsection{Different symmetries in the Kondo coupling and bath interaction}
One can also study the case when the bath interaction has \(p-\)wave symmetry:
\begin{equation}\begin{aligned}
	W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} =& \frac{1}{2}W f_\mathcal{P}\left(\pi + {\bf q}, {\bf k}_2, {\bf k}_1, {\bf q}\right) ~,\\
	=& -\frac{1}{2}Wf_\mathcal{P}\left({\bf k}_1, {\bf k}_2\right)~.
\end{aligned}\end{equation}
This choice does not preserve the momentum-dependence of the Kondo coupling, because we can no longer pull out a factor of \(f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)\) from the RG equation. At the first step, the RG equation is of the form
\begin{equation}\begin{aligned}
	&\Delta J^{(0)}_{{\bf k}_1, {\bf k}_2} =\\
	&-\sum_{{\bf q} \in \text{PS}} \frac{f_\mathcal{D}({\bf q})^2\left[{J}^2 f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf k}_1) + 2JW f_\mathcal{P}\left({\bf k}_1, {\bf k}_2\right)\right] }{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{4}}~.
\end{aligned}\end{equation}
The presence of the \(f_\mathcal{P}\) function in the second term leads to a new \(k-\)space dependence of the Kondo coupling at the second step, hence leading to a modified RG equation if one makes the \(k-\)dependence explicit.

@@

	\includegraphics[width=0.4\textwidth]{luttinger_top_change.png}

>>>>

\section{Philosophy of auxiliary model methods}
The present method is a realisation of the general method of using simpler systems called auxiliary models to study bulk systems~\cite{martin_2016}. In general, a full Hamiltonian can be separated into the Hamiltonians for a particular subsystem \(S\), the rest of the system \(R\), and the interactions between \(S\) and \(R\).
\begin{equation}\begin{aligned}
	\mathcal{H} &= \mathcal{H}_S\ket{S}\bra{S} + \mathcal{H}_R \ket{R}\bra{R} + \mathcal{H}_{SR} \ket{S}\bra{R} \\
				&+ \mathcal{H}_{RS}\ket{S}\bra{R} = \begin{bmatrix} & \mathcal{H}_{R} && \mathcal{H}_{RS} & \\ & \mathcal{H}_{RS}^* && \mathcal{H}_{S} & \end{bmatrix}
\end{aligned}\end{equation}
where \(\ket{S}\) and \(\ket{R}\) actually represents sums over all basis kets of \(S\) and \(R\) respectively. As an example, we can split the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice into three parts \(H_\text{hubb} = H_S + H_R + H_{SR} + H_{RS}\) (fig.~\ref{cluster-bath}), where
\begin{equation}\begin{aligned}
	H_S &= U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}\\
	H_R &= U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} \\
		&-t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right) \\
	H_{SR} + H_{Rs} &= - t^H\sum_{\sigma,\atop{i \in \text{N.N. of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)~.
\end{aligned}\end{equation}
The Greens function of the full Hamiltonian can also be split in a similar fashion:
\begin{equation}\begin{aligned}
	G(\omega) = \begin{bmatrix} G_S && G_{SR} \\ G_{RS} && G_R \end{bmatrix}
\end{aligned}\end{equation}
Each Greens function can be written in terms of the non-interacting counterpart and the self-energy through the Dyson equation: \(\Sigma_i = 1/G_{i,0} - 1/G_i\).

@@

\subsubsection{Same symmetries in the Kondo coupling and bath interaction}
Assuming that both the Kondo interaction and the bath interaction couple to the \(d-\)wave channel, we have the microscopic functional forms 
\begin{equation}\begin{aligned}
	J^{(0)}_{{\bf k},{\bf q}} &= J f_\mathcal{D}({\bf k}) f_\mathcal{D}({\bf q})~,\\
	J^{(0)}_{{\bf \bar q},{\bf q}} &= J f_\mathcal{D}(\pi + {\bf q}) f_\mathcal{D}({\bf q}) = Jf_\mathcal{D}({\bf q})^2 ~,
\end{aligned}\end{equation}
and
\begin{equation}\begin{aligned}
	W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} = W f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf q})^2~,
\end{aligned}\end{equation}
where \(f_\mathcal{D}({\bf k}) = \cos\left( ak_{x} \right) - \cos\left( ak_y \right) \) is the \(d-\)wave symmetric functional form in \(k-\)space
The numerator of the RG equations becomes
\begin{equation}\begin{aligned}
	f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf q})^4\left[J^2 + 4JW\right] ~.
\end{aligned}\end{equation}
Since a factor of \(f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)\) factors out of the RG equation, the Kondo coupling will preserve its momentum dependence during the RG equation, and we can study the RG flow of the amplitude \(J\):
\begin{equation}\begin{aligned}
	\Delta J = \sum_{{\bf q} \in \text{PS}} \frac{-\left(J^2 + 4JW\right) f_\mathcal{D}({\bf q})^4}{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{2}f_\mathcal{D}({\bf q})^4}~.
\end{aligned}\end{equation}

\subsubsection{Different symmetries in the Kondo coupling and bath interaction}
One can also study the case when the bath interaction has \(p-\)wave symmetry:
\begin{equation}\begin{aligned}
	W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} =& \frac{1}{2}W f_\mathcal{P}\left(\pi + {\bf q}, {\bf k}_2, {\bf k}_1, {\bf q}\right) ~,\\
	=& -\frac{1}{2}Wf_\mathcal{P}\left({\bf k}_1, {\bf k}_2\right)~.
\end{aligned}\end{equation}
This choice does not preserve the momentum-dependence of the Kondo coupling, because we can no longer pull out a factor of \(f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)\) from the RG equation. At the first step, the RG equation is of the form
\begin{equation}\begin{aligned}
	&\Delta J^{(0)}_{{\bf k}_1, {\bf k}_2} =\\
	&-\sum_{{\bf q} \in \text{PS}} \frac{f_\mathcal{D}({\bf q})^2\left[{J}^2 f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf k}_1) - 2JW f_\mathcal{P}\left({\bf k}_1, {\bf k}_2\right)\right] }{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{4}}~.
\end{aligned}\end{equation}
The presence of the \(f_\mathcal{P}\) function in the second term leads to a new \(k-\)space dependence of the Kondo coupling at the second step, hence leading to a modified RG equation if one makes the \(k-\)dependence explicit.

@@

	\includegraphics[width=0.4\textwidth]{windingNumbers.pdf}
